The Splashback Radius of Planck-SZ clusters

### 2018-11-14 Paper_new/RSP_paper_new.tex
edited affiliations

\author{
Dominik Zürcher \altaffilmark{1, 2}
Surhud More \altaffilmark{1, 3}, 
}
\affil{
$^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), \\ 
$^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
$^{3}$The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583\\
}

\begin{abstract}
We present evidence for the existence of the splashback radius
in galaxy clusters selected using the Sunyaev-Zeldovich effect.
We show that the deprojected cross-correlation of galaxy clusters
found in the Planck survey with galaxies detected photometrically in
the Pan-STARRS survey, shows a sharp steepening feature (a
logarithmic slope steeper than $-3$), which we associate with the
splashback radius.  We infer the three-dimensional splashback radius
for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$ $\mpch$,
where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.
The inferred value of the splashback radius is consistent with the
expected location for dark matter halos in the standard cold dark
matter paradigm. However, given the limited precision of our
measurements, we cannot conclusively rule out the smaller splashback
radius measured so far in the literature for photometrically
selected galaxy clusters. We show that the splashback radius does
not depend upon the galaxy magnitude for galaxies fainter than
$M_i-5\log h=-19.44$, and is present at a consistent location in
galaxy populations divided by color. The presence of the splashback radius in
the blue galaxy population could potentially be used to put lower limits on the
quenching timescales for galaxies. However, these results need further
verification with deeper datasets, as photometric errors could cause
contamination of blue galaxies with red galaxies.

>>>>

\author{
Dominik Zürcher \altaffilmark{1, 2}
Surhud More \altaffilmark{3, 1}, 
}
\affil{
$^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583, Japan \\ 
$^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
$^{4}$The Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411007, India
}

\begin{abstract}
We present evidence for the existence of the splashback radius in
galaxy clusters selected using the Sunyaev-Zeldovich effect.  We show
that the deprojected cross-correlation of galaxy clusters found in the
Planck survey with galaxies detected photometrically in the Pan-STARRS
survey, shows a sharp steepening feature (a logarithmic slope steeper
than $-3$), which we associate with the splashback radius. We infer
the three-dimensional splashback radius for the SZ cluster sample to
be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, where the cluster sample
has an average halo mass $M_{\rm 500c}=3.0\times10^{14}\msunh$ at an
average redshift of $z=0.18$.  The inferred value of the splashback
radius is consistent with the expected location for dark matter halos
in the standard cold dark matter paradigm. However, given the limited
precision of our measurements, we cannot conclusively rule out the
smaller splashback radius measured so far in the literature for
optically selected galaxy clusters. We show that the splashback radius
does not depend upon the galaxy magnitude for galaxies fainter than
$M_i-5\log h=-19.44$, and is present at a consistent location in
galaxy populations divided by color. The presence of the splashback
radius in the star-forming galaxy population could potentially be used
to put lower limits on the quenching timescales for galaxies. However,
these results need further verification with deeper datasets, as
photometric errors could cause contamination of the star-forming
galaxies by quenched galaxies.
